Growth Resilience

### 2017-06-21 analysis/analysis_resilience_bai.Rmd
Resilience anovas

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
library("stringr")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('pander')
```

@@

@@

# Plots Crecimiento
```{r}
gsj <- res_3_sj$growth %>% mutate(site='SJ')
gcaL <- res_3_caL$growth %>% mutate(site='caL')
gcaH <- res_3_caH$growth %>% mutate(site='caH')

@@

@@

```{r}
g %>% 
  mutate(disturb = recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.2) +
  geom_point(size=2, shape=21, fill='white') + 
  facet_grid(site~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())
```

@@

# Plots Resiliencia
```{r}
rsj <- res_3_sj$resilience %>% mutate(site='SJ')
rcaL<- res_3_caL$resilience %>% mutate(site='caL')
rcaH <- res_3_caH$resilience %>% mutate(site='caH')

re <- bind_rows(rsj, rcaL, rcaH)

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
library("stringr")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('pander')
library('broom')
library('effects')
```

@@

```{r}
aux_coefs %>% pander()
```

@@

# Plots Crecimiento
## Boxplot with outliers 
```{r}
gsj <- res_3_sj$growth %>% mutate(site='SJ')
gcaL <- res_3_caL$growth %>% mutate(site='caL')
gcaH <- res_3_caH$growth %>% mutate(site='caH')

@@

# Export csv 
write.csv(g, file=paste0(di, 'data/resilience/crecimientos_drought.csv'), row.names = FALSE)

@@

## Mean + se 
```{r}
g %>% 
  mutate(disturb = recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.2) +
  geom_point(size=2, shape=21, fill='white') + 
  facet_grid(site~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())
```

```{r}
pgrowht <- g %>% 
  mutate(disturb = recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb, colour=site)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.15) +
  geom_point(size=3, aes(shape=site), fill='white') + 
  geom_line(aes(group=site))+
  facet_wrap(~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())

pgrowht
ggsave(plot=pgrowht, width=8, height = 4,
       filename=paste0(di, 'out/fig/resilience/bai_events.pdf')) 
```

@@

# Anovas Resiliencia

```{r}
# Prepara data 
rsj <- res_3_sj$resilience %>% mutate(site='SJ')
rcaL<- res_3_caL$resilience %>% mutate(site='caL')
rcaH <- res_3_caH$resilience %>% mutate(site='caH')

re <- bind_rows(rsj, rcaL, rcaH)
re$disturb_year <- as.factor(re$disturb_year)
re$site <- as.factor(re$site)

# Export csv 
write.csv(re, file=paste0(di, 'data/resilience/resilience_bai.csv'), row.names = FALSE)
```

## Custom functions

```{r}
# Custom Function to compute ANOVAS
aovas <- function(df, vars, resp_var){ 
  require('dplyr')
  require('broom')

  # Create subset 
  dfsel <- df %>% dplyr::select_(.dots=c(vars, resp_var))

  # Model 
  myformula <- as.formula(paste0(resp_var,  " ~ ",
                                 paste(vars, collapse = '*')))

  mymodel <- aov(myformula, data=dfsel)

  # Output model Summary http://my.ilstu.edu/~wjschne/444/ANOVA.html#(1)
  model_coeff <- broom::tidy(mymodel)
  model_summary <- broom::glance(mymodel)

  out <- c() 
  out$model_coeff <- model_coeff
  out$model_summary <- model_summary
  out$mymodel <- mymodel

  return(out)
}

# Post-Hoc comparison
phc <- function(mymodel, resp_var){
  require(lsmeans)

  # Disturb Event 
  ph_event <- lsmeans(mymodel, pairwise ~ disturb_year, adjust = "tukey")

  # differences letters 
  cld_event <- cld(ph_event, alpha   = 0.01, 
                   Letters = letters, 
                   adjust  = "tukey")

  # Site  
  ph_site <- lsmeans(mymodel, pairwise ~ site, adjust = "tukey")
  cld_site <- cld(ph_site, alpha   = 0.01, 
                 Letters = letters, 
                 adjust  = "tukey")

  # interaction 
  ph_i <- lsmeans(mymodel, pairwise ~ disturb_year:site, adjust = "tukey")

  # Objets for plot
  aux_ph_site <- as.data.frame(summary(ph_site$lsmeans)) 
  aux_ph_site <- aux_ph_site %>% mutate(var = resp_var)
  aux_ph_event <- as.data.frame(summary(ph_event$lsmeans)) 
  aux_ph_event <- aux_ph_event %>% mutate(var = resp_var)
  aux_ph_i <- as.data.frame(summary(ph_i$lsmeans)) 
  aux_ph_i <- aux_ph_i %>% mutate(var = resp_var)

  # Return objects
  cat('\n### Event ###\n')
  print(ph_event)
  print(cld_event)
  cat('\n### Clu pop ###\n')
  print(ph_site)
  print(cld_site)
  cat('\n### Event:Clu pop ###\n')
  print(ph_i)
  return(list(aux_ph_site, aux_ph_event, aux_ph_i))
}
```

```{r}
vars <- c('disturb_year','site')
```

## Recovery 
```{r}
# Variable
resp_var <- 'rc'

# AOV
aov_rc <- aovas(re, vars=vars, resp_var = resp_var)
```

```{r}
mc <- aov_rc$model_coeff

pander(mc, round=5,
       caption = paste0("ANOVA table: ", resp_var), missing = '', 
       emphasize.strong.cells = 
         which(mc < 0.1 & mc == mc$p.value, arr.ind = T))
```

```{r}
gm <- aov_rc$model_summary

gm <- apply(gm, 1, formatC, digits = 2, format = "f") %>% t()
colnames(gm) <- paste0("$",c("R^2","\\mathrm{adj}R^2","\\sigma_e","F","p","df_m","\\mathrm{logLik}","AIC","BIC","\\mathrm{dev}","df_e"),"$")
rownames(gm) <- "Statistic"
pander(t(gm)) 
```

### Post hoc comparison

```{r}
# Post hoc Define model
mymodel <- aov_rc$mymodel
postH_rc <- phc(mymodel = mymodel, resp_var = resp_var)
```

### Plots

```{r}
#### ~ Site
ps <- plot(effect("site",mymodel))
#### ~ Disturb Year
pd <- plot(effect('disturb_year', mymodel))
#### Disturb Year:Site
picollapse <- plot(effect("disturb_year:site",mymodel), multiline = TRUE, ci.style = 'bars')
pi <- plot(effect("disturb_year:site",mymodel), layout=c(3,1))
```

```{r}
ps
```

```{r}
pd
```

```{r}
picollapse
```

```{r}
pi
```

## Resistance 
```{r}
# Variable
resp_var <- 'rt'

# AOV
aov_rt <- aovas(re, vars=vars, resp_var = resp_var)
```

```{r}
mc <- aov_rt$model_coeff

pander(mc, round=5,
       caption = paste0("ANOVA table: ", resp_var), missing = '', 
       emphasize.strong.cells = 
         which(mc < 0.1 & mc == mc$p.value, arr.ind = T))
```

```{r}
gm <- aov_rt$model_summary

gm <- apply(gm, 1, formatC, digits = 2, format = "f") %>% t()
colnames(gm) <- paste0("$",c("R^2","\\mathrm{adj}R^2","\\sigma_e","F","p","df_m","\\mathrm{logLik}","AIC","BIC","\\mathrm{dev}","df_e"),"$")
rownames(gm) <- "Statistic"
pander(t(gm)) 
```

### Post hoc comparison

```{r}
# Post hoc Define model
mymodel <- aov_rt$mymodel
postH_rc <- phc(mymodel = mymodel, resp_var = resp_var)
```

### Plots

```{r}
#### ~ Site
ps <- plot(effect("site",mymodel))
#### ~ Disturb Year
pd <- plot(effect('disturb_year', mymodel))
#### Disturb Year:Site
picollapse <- plot(effect("disturb_year:site",mymodel), multiline = TRUE, ci.style = 'bars')
pi <- plot(effect("disturb_year:site",mymodel), layout=c(3,1))
```

```{r}
ps
```

```{r}
pd
```

```{r}
picollapse
```

```{r}
pi
```

## Relative Resilience 
```{r}
# Variable
resp_var <- 'rrs'

# AOV
aov_rrs <- aovas(re, vars=vars, resp_var = resp_var)
```

```{r}
mc <- aov_rrs$model_coeff

pander(mc, round=5,
       caption = paste0("ANOVA table: ", resp_var), missing = '', 
       emphasize.strong.cells = 
         which(mc < 0.1 & mc == mc$p.value, arr.ind = T))
```

```{r}
gm <- aov_rrs$model_summary

gm <- apply(gm, 1, formatC, digits = 2, format = "f") %>% t()
colnames(gm) <- paste0("$",c("R^2","\\mathrm{adj}R^2","\\sigma_e","F","p","df_m","\\mathrm{logLik}","AIC","BIC","\\mathrm{dev}","df_e"),"$")
rownames(gm) <- "Statistic"
pander(t(gm)) 
```

### Post hoc comparison

```{r}
# Post hoc Define model
mymodel <- aov_rrs$mymodel
postH_rc <- phc(mymodel = mymodel, resp_var = resp_var)
```

### Plots

```{r}
#### ~ Site
ps <- plot(effect("site",mymodel))
#### ~ Disturb Year
pd <- plot(effect('disturb_year', mymodel))
#### Disturb Year:Site
picollapse <- plot(effect("disturb_year:site",mymodel), multiline = TRUE, ci.style = 'bars')
pi <- plot(effect("disturb_year:site",mymodel), layout=c(3,1))
```

```{r}
ps
```

```{r}
pd
```

```{r}
picollapse
```

```{r}
pi
```

## Resilience 
```{r}
# Variable
resp_var <- 'rs'

# AOV
aov_rs <- aovas(re, vars=vars, resp_var = resp_var)
```

```{r}
mc <- aov_rs$model_coeff

pander(mc, round=5,
       caption = paste0("ANOVA table: ", resp_var), missing = '', 
       emphasize.strong.cells = 
         which(mc < 0.1 & mc == mc$p.value, arr.ind = T))
```

```{r}
gm <- aov_rs$model_summary

gm <- apply(gm, 1, formatC, digits = 2, format = "f") %>% t()
colnames(gm) <- paste0("$",c("R^2","\\mathrm{adj}R^2","\\sigma_e","F","p","df_m","\\mathrm{logLik}","AIC","BIC","\\mathrm{dev}","df_e"),"$")
rownames(gm) <- "Statistic"
pander(t(gm)) 
```

### Post hoc comparison

```{r}
# Post hoc Define model
mymodel <- aov_rs$mymodel
postH_rc <- phc(mymodel = mymodel, resp_var = resp_var)
```

### Plots

```{r}
#### ~ Site
ps <- plot(effect("site",mymodel))
#### ~ Disturb Year
pd <- plot(effect('disturb_year', mymodel))
#### Disturb Year:Site
picollapse <- plot(effect("disturb_year:site",mymodel), multiline = TRUE, ci.style = 'bars')
pi <- plot(effect("disturb_year:site",mymodel), layout=c(3,1))
```

```{r}
ps
```

```{r}
pd
```

```{r}
picollapse
```

```{r}
pi
```
